The Impact of Education <br>

### 2014-12-04 Presentation/EdEntrePres.Rmd
Added final map and chart for FearFail.  Next step is adding two more Zelig charts (format is already set)

>>>>

## Variation in Fear Perception in OECD Countries

# Import GEM data frame
PercentFear <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_FearFail.csv", header = TRUE, cache = FALSE, na.strings = "-")

## Add country codes and place new column at beginning of the data frame
# Create a vector of country codes
F2 <- countrycode(PercentFear$Country, "country.name", "iso2c")

# Create a new column and insert the country code vector
PercentFear$new.col <- F2

# Reorder columns so country code is first
F3 <- PercentFear[,c(15,1:14)]

# Rename first column
F4 <- plyr::rename(x = F3, 
                   replace = c("new.col" = "iso2c"))

# Remove X's in D4 year columns
names(F4) <- gsub("X", "", names(F4))

# Set columns as numeric
F4[,"2001"] <- as.numeric(F4[,"2001"])
F4[,"2002"] <- as.numeric(F4[,"2002"])
F4[,"2003"] <- as.numeric(F4[,"2003"])
F4[,"2004"] <- as.numeric(F4[,"2004"])
F4[,"2005"] <- as.numeric(F4[,"2005"])
F4[,"2006"] <- as.numeric(F4[,"2006"])
F4[,"2007"] <- as.numeric(F4[,"2007"])
F4[,"2008"] <- as.numeric(F4[,"2008"])
F4[,"2009"] <- as.numeric(F4[,"2009"])
F4[,"2010"] <- as.numeric(F4[,"2010"])
F4[,"2011"] <- as.numeric(F4[,"2011"])
F4[,"2012"] <- as.numeric(F4[,"2012"])
F4[,"2013"] <- as.numeric(F4[,"2013"])

# Save cleaned df
Fear1 <- F4

# Generate a new column with mean of all other columns
F4$mean <- rowMeans(subset(F4, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
                                          "2009", "2010", "2011", "2012", "2013")), na.rm = TRUE)

# Drop year columns, leaving only mean column
F4$'2001' <- NULL
F4$'2002' <- NULL
F4$'2003' <- NULL
F4$'2004' <- NULL
F4$'2005' <- NULL
F4$'2006' <- NULL
F4$'2007' <- NULL
F4$'2008' <- NULL
F4$'2009' <- NULL
F4$'2010' <- NULL
F4$'2011' <- NULL
F4$'2012' <- NULL
F4$'2013' <- NULL

# Create 
F4[, 3] <- round(log(F4[, 3]), digits = 2)
```

# Plot perceived opportunties map
FF_map <- gvisGeoChart(F4, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#ece7f2', '#2b8cbe']"
))

# Duplicate F4 (perceived opportunities) df
DroppedF4 <- F4

# Drop iso2c in Dropped4
DroppedF4$iso2c <- NULL

# Print the table
print(FF_map, tag = 'chart')

## Variation in Fear of Failure
```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library("ggplot2")
library("reshape2")

# Subset Opp2
Fear2 <- subset(Fear1, iso2c %in% myvars2)

# Melt Opp2 df
Fear3 <- melt(data = Fear2,
                  id.vars = c("Country", "iso2c"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

# Edit column names
names(Fear3) <- gsub("value", "FearFail", names(Fear3))
names(Fear3) <- gsub("variable", "Year", names(Fear3))

Fear3$iso2c <- NULL
```

# Create plot
ggplot(Fear3,aes(x = Year, y = FearFail, colour = Country, group = Country)) + geom_line()

## Regression Results

We decided to ignore country-specific effects because the change in the intercept resulting from fixed effects was small and the slope of the fixed effects and OLS models are very similar.
